---
title: "Demographic Trait Overview"
author: "Matt Robertson"
date: "07/05/2021"
output: 
 github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)

setwd("Data")

abun<-read.csv(file="abundance.csv", header = TRUE)
bio<-read.csv(file="biomass.csv", header = TRUE)
len<-read.csv(file="l_at_mat.csv", header = TRUE)
```

We are currently collecting data on abundance, biomass, and length at maturity for fish stocks around Newfoundland and Labrador. Based on our data inputs it should be possible to separate each time-series into stocks, species, divisions, and functional groups. The end goal will be to assess these time-series using dynamic factor analysis (DFA) and compare the trends to environmental trends to identify if there are similarities in how these stocks demographies have shifted over time and whether shared changes can be related to environmental variables.

# Length at maturity Data

```{r, echo=FALSE}

#cut out the column for years
years<-len[,1]

#pull out the names of the stocks (just column names)
stocks<-colnames(len[,2:length(len)])
#separate species names (only works if people input stock names following definition in metadata)
spp<-unlist(lapply(strsplit(stocks, "_"),`[[`, 1))
#separate divisions (only works if people input stock names following definition in metadata)
divs<-unlist(sapply(strsplit(stocks, "_"),tail, 1))

#identify the unique species
unique_spp<-unique(spp)
#these need to be input manually, I have been basing the functional group on definitions in the SI of Dempsey et al. (2017)
# https://doi.org/10.1016/j.ecolind.2016.12.011
uni_fxnal_group<-c("planktivore","benthivore","benthivore","benthivore","planktivore","benthivore") 
#this replaces the name of each species with the name of its functional group
fxnal_group<-gsub(unique_spp[1],uni_fxnal_group[1],
                  gsub(unique_spp[2],uni_fxnal_group[2],
                      gsub(unique_spp[3],uni_fxnal_group[3],
                          gsub(unique_spp[4],uni_fxnal_group[4],
                             gsub(unique_spp[5],uni_fxnal_group[5],
                                  gsub(unique_spp[6],uni_fxnal_group[6],spp))))))

#scale each of the lengths at maturity
scaled_abun<-apply(len[,2:length(len)], 2, scale)

#combine all of the different tpyes of data into one dataframe
abun_df<-data.frame(abun=c(scaled_abun),year=rep(years, length(scaled_abun[1,])), stock=rep(stocks, each=length(years)), 
                          spp=rep(spp, each=length(years)), fxnal_group= rep(fxnal_group, each=length(years)),
                          div=rep(divs, each=length(years)))

```


## NAFO Division {.tabset .tabset-fade .tabset-pills}

### All

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year), FUN=median, na.rm=TRUE)

ggplot()+
  geom_line(data=abun_df,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=abun_df,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=agg_spp, aes(x=Group.1, y=x))+
  geom_point(data=agg_spp, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 2J3K

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")

ggplot()+
  geom_line(data=xs$`2J3K`,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=xs$`2J3K`,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=th_sk, aes(x=Group.1, y=x))+
  geom_point(data=th_sk, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3LNO

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")

ggplot()+
  geom_line(data=xs$`3LNO`,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=xs$`3LNO`,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=th_sk, aes(x=Group.1, y=x))+
  geom_point(data=th_sk, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3Ps

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")

ggplot()+
  geom_line(data=xs$`3Ps`,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=xs$`3Ps`,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=th_sk, aes(x=Group.1, y=x))+
  geom_point(data=th_sk, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 4RST

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4R")

ggplot()+
  geom_line(data=xs$`4R`,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=xs$`4R`,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=th_sk, aes(x=Group.1, y=x))+
  geom_point(data=th_sk, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


## Functional Group {.tabset .tabset-fade .tabset-pills}

### Benthivore

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$fxnal_group)

agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$fxnal_group), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="benthivore")

ggplot()+
  geom_line(data=xs$benthivore,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=xs$benthivore,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=th_sk, aes(x=Group.1, y=x))+
  geom_point(data=th_sk, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


### Planktivore

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}

agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$fxnal_group), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="planktivore")

ggplot()+
  geom_line(data=xs$planktivore,aes(x =year, y=abun, group = stock), colour="grey")+
  geom_point(data=xs$planktivore,aes(x =year, y=abun, group = stock),colour="grey")+
  geom_line(data=th_sk, aes(x=Group.1, y=x))+
  geom_point(data=th_sk, aes(x=Group.1, y=x))+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

## Species Overview {.tabset .tabset-fade .tabset-pills}

### American plaice

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="Americanplaice") #change the name here
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```
#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Americanplaice") #change the name here
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Atlantic Mackerel

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="AtlanticMakerel")
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="AtlanticMakerel")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Herring

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Herring")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Herring")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Roughhead Grenadier

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Roughheadgrenadier")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Roughheadgrenadier")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Witch flounder

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Witchflounder")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Witchflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Yellowtail flounder

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="Yellowtailflounder")
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled length at maturity")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```



# Abundance Data

```{r, echo=FALSE}

years<-abun[,1]

stocks<-colnames(abun[,2:8])
spp<-unlist(lapply(strsplit(stocks, "_"),`[[`, 1))
divs<-unlist(sapply(strsplit(stocks, "_"),tail, 1))

spp<-gsub("YellowtailFlounder","Yellowtailflounder",spp)

unique_spp<-unique(spp)
uni_fxnal_group<-c("benthivore","benthivore")
fxnal_group<-gsub(unique_spp[1],uni_fxnal_group[1],gsub(unique_spp[2],uni_fxnal_group[2],spp))

scaled_abun<-apply(abun[,2:8], 2, scale)

abun_df<-data.frame(abun=c(scaled_abun),year=rep(years, length(scaled_abun[1,])), stock=rep(stocks, each=length(years)), 
                          spp=rep(spp, each=length(years)), fxnal_group= rep(fxnal_group, each=length(years)),
                          div=rep(divs, each=length(years)))

```

## Species Overview {.tabset .tabset-fade .tabset-pills}

### Thorny skate

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Thornyskate")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Yellowtail flounder

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="Yellowtailflounder")
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

## NAFO Division {.tabset .tabset-fade .tabset-pills}

### 2J3K

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`2J3K`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3LNO

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3LNO`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3Ps

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3Ps`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 4RST

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`4RST`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


# Biomass Data

```{r, echo=FALSE}

years<-bio[,1]

stocks<-colnames(bio[,2:8])
spp<-unlist(lapply(strsplit(stocks, "_"),`[[`, 1))
divs<-unlist(sapply(strsplit(stocks, "_"),tail, 1))

spp<-gsub("YellowtailFlounder","Yellowtailflounder",spp)

unique_spp<-unique(spp)
uni_fxnal_group<-c("benthivore","benthivore")
fxnal_group<-gsub(unique_spp[1],uni_fxnal_group[1],gsub(unique_spp[2],uni_fxnal_group[2],spp))

scaled_abun<-apply(bio[,2:8], 2, scale)

abun_df<-data.frame(abun=c(scaled_abun),year=rep(years, length(scaled_abun[1,])), stock=rep(stocks, each=length(years)), 
                          spp=rep(spp, each=length(years)), fxnal_group= rep(fxnal_group, each=length(years)),
                          div=rep(divs, each=length(years)))

```

## Species Overview {.tabset .tabset-fade .tabset-pills}

### Thorny skate

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Thornyskate")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Yellowtail flounder

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="Yellowtailflounder")
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

## NAFO Division {.tabset .tabset-fade .tabset-pills}

### 2J3K

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`2J3K`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3LNO

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3LNO`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3Ps

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3Ps`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 4RST

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`4RST`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```
