---
title: "Demographic Trait Overview"
author: "Matt Robertson"
date: "07/05/2021"
output: 
 github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)

setwd("Data")

abun<-read.csv(file="abundance.csv", header = TRUE)
bio<-read.csv(file="biomass.csv", header = TRUE)
len<-read.csv(file="l_at_mat.csv", header = TRUE)
```

We are currently collecting data on abundance, biomass, and length at maturity for fish stocks around Newfoundland and Labrador. Based on our data inputs it should be possible to separate each time-series into stocks, species, divisions, and functional groups. The end goal will be to assess these time-series using dynamic factor analysis (DFA) and compare the trends to environmental trends to identify if there are similarities in how these stocks demographies have shifted over time and whether shared changes can be related to environmental variables.

# Abundance Data

```{r, echo=FALSE}

years<-abun[,1]

stocks<-colnames(abun[,2:8])
spp<-unlist(lapply(strsplit(stocks, "_"),`[[`, 1))
divs<-unlist(sapply(strsplit(stocks, "_"),tail, 1))

spp<-gsub("YellowtailFlounder","Yellowtailflounder",spp)

unique_spp<-unique(spp)
uni_fxnal_group<-c("benthivore","benthivore")
fxnal_group<-gsub(unique_spp[1],uni_fxnal_group[1],gsub(unique_spp[2],uni_fxnal_group[2],spp))

scaled_abun<-apply(abun[,2:8], 2, scale)

abun_df<-data.frame(abun=c(scaled_abun),year=rep(years, length(scaled_abun[1,])), stock=rep(stocks, each=length(years)), 
                          spp=rep(spp, each=length(years)), fxnal_group= rep(fxnal_group, each=length(years)),
                          div=rep(divs, each=length(years)))

```

## Species Overview {.tabset .tabset-fade .tabset-pills}

### Thorny skate

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Thornyskate")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Yellowtail flounder

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="Yellowtailflounder")
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

## NAFO Division {.tabset .tabset-fade .tabset-pills}

### 2J3K

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`2J3K`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3LNO

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3LNO`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3Ps

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3Ps`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 4RST

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`4RST`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Abundance")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


# Biomass Data

```{r, echo=FALSE}

years<-bio[,1]

stocks<-colnames(bio[,2:8])
spp<-unlist(lapply(strsplit(stocks, "_"),`[[`, 1))
divs<-unlist(sapply(strsplit(stocks, "_"),tail, 1))

spp<-gsub("YellowtailFlounder","Yellowtailflounder",spp)

unique_spp<-unique(spp)
uni_fxnal_group<-c("benthivore","benthivore")
fxnal_group<-gsub(unique_spp[1],uni_fxnal_group[1],gsub(unique_spp[2],uni_fxnal_group[2],spp))

scaled_abun<-apply(bio[,2:8], 2, scale)

abun_df<-data.frame(abun=c(scaled_abun),year=rep(years, length(scaled_abun[1,])), stock=rep(stocks, each=length(years)), 
                          spp=rep(spp, each=length(years)), fxnal_group= rep(fxnal_group, each=length(years)),
                          div=rep(divs, each=length(years)))

```

## Species Overview {.tabset .tabset-fade .tabset-pills}

### Thorny skate

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
th_sk<-subset(abun_df, spp=="Thornyskate")
ggplot(th_sk, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Thornyskate")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### Yellowtail flounder

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
yt_fl<-subset(abun_df, spp=="Yellowtailflounder")
ggplot(yt_fl, aes(x=year, y=abun))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  facet_wrap(~stock)+
    theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$spp), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="Yellowtailflounder")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

## NAFO Division {.tabset .tabset-fade .tabset-pills}

### 2J3K

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`2J3K`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="2J3K")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3LNO

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3LNO`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3LNO")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 3Ps

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`3Ps`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="3Ps")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

### 4RST

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
xs <- split(abun_df,f = abun_df$div)

ggplot(xs$`4RST`,aes(x =year, y=abun,group = stock)) + 
  geom_line(colour="grey")+
  geom_point(colour="grey")+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~spp)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```


#### Aggregated Mean

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=mean, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```

#### Aggregated Median

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4}
agg_spp<-aggregate(abun_df$abun, by=list(abun_df$year, abun_df$div), FUN=median, na.rm=TRUE)
th_sk<-subset(agg_spp, Group.2=="4RST")
ggplot(th_sk, aes(x=Group.1, y=x))+
  geom_line()+
  geom_point()+
  xlab("Year")+ylab("Scaled Biomass")+
  #facet_wrap(~Group.2)+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle=45, hjust=1))
```
